What Can Stack Traces Tell us about Exceptions in Java?

### 2014-07-07 android-stacks.tex
more changes process description - section III and subsections

This work describes an exploratory study which was based on a sequential
mixed-methods approach~\cite{ivankova2006using} for collecting, analyzing, and
integrating both quantitative and qualitative evidence along the stages of the
research process. The main goal of this study was to gain a better understanding
of the use of exceptions in Java programs based mainly on the information
available on exception stack traces. The exceptions available on exception stack trace
are not limited to the exceptions expliciltly thrown by the Java developer but also include
the exceptions implicitly thrown by the JVM during the program execution,
due to a programming error (e.g., out-of-bounds array index, division-by-zero, 
access to a null reference) or an internal error or resource limitation (e.g.,
OutofMemoryError).

@@

%For RQ3 we investigate
%quantitatively and highlight interesting cases by exploring cases qualitatively.
Figure~\ref{fig:overviewfig} presents an overview of the mixed-methods approach
conducted to answer these questions.

@@

\subsection{Study Context and Github Data}
\label{sec:git}

 What is the prevalence of stack traces on reported issues?
   What are the most common exceptions?

\noindent\emph{Kinds of Analyzed Issues.} Issues on Github are different from
issues on dedicated bug tracking tools such as Bugzilla and Jira. The most
important difference is that there are no predefined fields for bug reporters to
select from (e.g. severity and priority); Github uses instead a more open ended
tagging system. Repositories are offered a pre-defined set of labels, but
repository owners can modify them at will. An issue can have an arbitrary set of
labels attached. Hence, this study does not restrict the analysis of stack
traces defined on defect-issues, based on the assumption that regardless of the
type of issue where its is defined the stack trace information contain relevant
information concerning the exception use. Moreover, issues and pull requests are
dual on Github; all pull requests have a corresponding ``backing'' issue which
are automatically generated. Therefore, we excluded pull request based
issues from our analysis. Finally, the Github API allows the automated
generation of issues for specific repositories, which automated tools often use
to report crashes. In some cases, this led to high number of issues that
included stack traces. We identified and filtered those cases out (e.g.,
the~\textsf{pullwifi} project was responsible for almost 50\% of all Android issues in our dataset).

@@

Prevalence or prevalence proportion, a term often used in epidemiology,
represents the proportion of a population found to have a particular condition
(e.g. a disease) over the total number of the studied population. In our work, we used
this term to evaluate a condition (i.e., presence of a stack trace) over issues
reported on GitHub repositories.

>>>>

This work describes an exploratory study which was based on a sequential
mixed-methods approach~\cite{ivankova2006using} for collecting, analyzing, and
integrating both quantitative and qualitative evidence along the stages of the
research process.

The main goal of this study was to gain a better understanding
of the use of exceptions in Java programs based mainly on the information
available on exception stack traces embedded on Github issues.
The exceptions available on exception stack trace are not limited to the exceptions 
expliciltly thrown by the Java developer but also include
the exceptions implicitly thrown by the JVM during the program execution,
due to a programming error (e.g., out-of-bounds array index, division-by-zero, 
access to a null reference) or an internal error or resource limitation (e.g.,
OutofMemoryError).

@@

\subsection{Github Data}
\label{sec:git}

As mentioned before, this study amined at mining information available on GitHub issues,
more specifically, extracting and distilling the stack traces embedded on GItHub issues.

Issues on Github are different from issues on dedicated bug tracking tools such as 
Bugzilla and Jira. The most important difference is that there are no predefined fields
  (e.g. severity and priority). Instead, Github uses a more open ended tagging system, on which
repositories are offered a pre-defined set of labels, but repository owners can modify 
them at will. Therefore, an issue may have none ore an arbitrary set of labels depending 
on which repository it was created.

Therefore, this study is based on the assumption if an stack trace information embedded
 in an issue, it contain relevant information concerning the exception use -  regardless the
 lables associated to the issue.

Moreover, issues and pull requests are dual on Github; all pull requests have a corresponding 
``backing'' issue which
are automatically generated. Therefore, we excluded such automatically generated
issues from our analysis. Finally, the Github API allows the automated
generation of issues for specific repositories, which automated tools often use
to report crashes. In some cases, this led to high number of issues that
included stack traces. We identified and filtered those cases out (e.g.,
the~\textsf{pullwifi} project was responsible for almost 50\% of all Android issues in our dataset).

This study used the dataset provided by the GHTorrent project~\cite{Gousi13}, an off-line mirror of the data 
offered through the Github API.  GHTorrent has been collecting data from Git since 
February 2012. Up to Dec 2013, and when we queried GHTorrent, it included 332,864 non-fork Java
repositories \footnote {A Java project is specified in GitHub with a
specific label.}  from which only 44,323 have contained at least issue report in their lifetime. From this set only 16,837 were watched by external users. To ensure that our work targets projects that are openly used by
users other than their developers, we focused our analysis on just those projects.

From this set of 16.836 Java projects which overall contained 356.057 issues, we retrieved the metadata related to each Java project (e.g., repository's names and short descriptions), and the content of every issue and issue comment and stored in a relational database.

Using the heuristics presented in Section~\ref{sec:android}, we selected 482 repositories featuring Android projects on which we perform manual inspection was performed.

\subsection{Study Context}

Before investigating the research questions listed above we analyzed the prevalence of stack traces 
on issues created on Github. Prevalence or prevalence proportion, a term often used in epidemiology,
represents the proportion of a population found to have a particular condition
(e.g. a disease) over the total number of the studied population. In our work, we used
this term to evaluate a condition (i.e., presence of a stack trace) over issues
reported on GitHub repositories.

\subsection{The Mining Process}
\label{sec:miningproc}

Figure~\ref{fig:overviewfig} presents an overview of the mixed-methods approach
conducted to answer these questions.

@@

@@
